Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-07-21 main.tex
SB_eff_g >= 24.5 definition
Updates from Overleaf

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\sbunit}{mag~arcsec$^{-2}$}

@@

\author[0000-0002-8873-5065]{Peter Melchior}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2704-5028]{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Shany Danieli}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

%% I'd like to invite Shany?

@@

\section{Methodology}
Given an overview of the steps here.

@@

    \item \textbf{Initial Sample Selection}. In this step, we take the output catalog from the previous step and remove those objects that are not likely to be LSBGs of interest. To be specific, we require objects have $g$-band half-light radius (measured by Source Extractor) larger than $r_{\rm min} = 2.0\arcsec$. We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$. %These cuts are the same as in \citetalias{Greco2018}. 
    \textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}

@@

\subsubsection{Measurement uncertainty}\label{sec:meas_unc}
We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}. Overall speaking, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$\sbunit is under-estiamted. We also characterize the bias and the scatter in measurement as a function of size and surface brightness. We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.

In order to test how well do we recover the photometric and structural parameters in the modeling step (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile. We compare the fitting results with the ground truth in Figure \ref{fig:meas_bias}, where $\Delta(X) = X(\rm truth) - X(\rm measured)$, and x-axis corresponds to the truth values. We find that the measured half-light radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and apparent size. For surface brightness fainter than 27\ \sbunit, the measured size can be much smaller than the truth. As a result, the apparent magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truth.

@@

Besides, it is also important to characterize the measurement uncertainty. The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, contamination effects, etc. Unlike other parametric modeling code such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimial solution. Thus we cannot get a statistical error of the measured properties from \code{scarlet}. However, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor. Following the same way of calculating the bias, in each bin, we compute the standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid. The measurement errors are shown in Figure \ref{fig:meas_err} as contours.

@@

After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left. Then we match them to the LSBG catalog (described in Section \ref{sec:detection}) as follows. For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}. It turns out that 40\% of hosts have virial radii larger than 300 kpc. Then we identify any LSBG that falls into the projected angular virial radius of the host. Then these LSBGs are associated with the host. We repeat this process for all hosts. If one LSBG is associated to multiple hosts, we assign it to the nearest host (normalized by the angular size of virial radius). Finally, we have 901 MW-like hosts and 8,367 LSBG candidates associated with them. However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shrreded large galaxies, compact sources in galaxy outskirts, etc. In the following, we perform a deblending step to effectively remove these spurious objects.

\subsection{UDG sample and UPG sample}
Remember to filter the UDG sample through the FDFC mask, and also remove duplicated objects.

@@

@@

\subsection{Quenched fraction}

@@

\begin{table}
\caption{UDG (UPG) catalog description} 
\label{tab:catalog}
\begin{center}
\begin{tabular}{l l l}
\hline\hline
% \multicolumn{3}{c}{Table: LSBGs (781 rows)}                 \\
% \hline
Column Name      & Unit    & Description                    \\
\hline
ID                       &         & Unique LSBG ID \\
ra                       & deg     & Right ascension (J2000) \\
dec                      & deg     & Declination (J2000) \\
$r_e$         & arcsec  & Circularized effective radius  \\
$\sigma(r_e)$ & arcsec  & Uncertainty of $r_e$ \\
$\overline{\mu}_{\mathrm{eff}}(g)$               & \sbunit & $g$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(g))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(g)$           \\
$\overline{\mu}_{\mathrm{eff}}(r)$               & \sbunit & $r$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
$\overline{\mu}_{\mathrm{eff}}(i)$               & \sbunit & $i$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
$m_g$                    & mag     & $g$-band apparent magnitude     \\
$\sigma(m_g)$            & mag     & Uncertainty of $m_g$            \\
$m_r$                    & mag     & $r$-band apparent magnitude     \\
$\sigma(m_r)$            & mag     & Uncertainty of $m_r$            \\
$m_i$                    & mag     & $i$-band apparent magnitude     \\
$\sigma(m_i)$            & mag     & Uncertainty of $m_i$            \\
$g-r$                    & mag     & $g-r$ color                     \\
$\sigma(g-r)$           & mag     & Uncertainty of $g-r$ color      \\
$g-i$                    & mag     & $g-i$ color                     \\
$\sigma(g-i)$           & mag     & Uncertainty of $g-i$ color      \\
$\nu$                    &         & Spergel index              \\
$\varepsilon$               &         & Ellipticity                     \\
$A_g$                    & mag     & $g$-band Galactic extinction \\
$A_r$                    & mag     & $r$-band Galactic extinction \\
$A_i$                    & mag     & $i$-band Galactic extinction \\
\hline\hline
\end{tabular}
\end{center}
\tablecomments{
These tables are published in their entirety in machine-readable format.
Magnitudes are on the AB system and have not been corrected for Galactic
extinction. We provide Galactic extinction corrections, which are derived from
the \citet{Schlafly2011} recalibration of the \citet{SFD1998} dust maps. 
}
\end{table}

>>>>

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
% \newcommand{\sbunit}{mag~arcsec$^{-2}$}
\newcommand{\sbunit}{\mathrm{mag\ arcsec}^{-2}}
\newcommand{\sbeff}{\overline{\mu}_{\mathrm{eff}}(g)}

@@

\author[0000-0002-1841-2252]{Rachael Beaton}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2991-9251]{Kirsten Casey}
\affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
\author[0000-0002-1841-2252]{Shany Danieli}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Andy Goulding}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2704-5028]{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Erin Kado-Fong}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-8873-5065]{Peter Melchior}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

@@

\section{LSBG search in HSC S18A}
Given an overview of the steps here.

@@

    \item \textbf{Initial Sample Selection}. In this step, we take the output catalog from the previous step and remove those objects that are not likely to be LSBGs of interest. To be specific, we require objects have $g$-band half-light radius (measured by Source Extractor) larger than $r_{\rm min} = 2.0\arcsec$. We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$. %These cuts are the same as in \citetalias{Greco2018}. 
    %\textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}

@@

\subsubsection{Measurement uncertainty}\label{sec:meas_unc}
We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}. Overall speaking, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27\ \sbunit$ is under-estiamted. We also characterize the bias and the scatter in measurement as a function of size and surface brightness. We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.

In order to test how well do we recover the photometric and structural parameters in the modeling step (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile. We compare the fitting results with the ground truth in Figure \ref{fig:meas_bias}, where $\Delta(X) = X(\rm truth) - X(\rm measured)$, and x-axis corresponds to the truth values. We find that the measured half-light radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and apparent size. For surface brightness fainter than $27\ \sbunit$, the measured size can be much smaller than the truth. As a result, the apparent magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truth.

@@

Besides, it is also important to characterize the measurement uncertainty. The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, contamination effects, etc. Unlike other parametric modeling code such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimal solution. Thus we cannot get a statistical error of the measured properties from \code{scarlet}. However, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor. Following the same way of calculating the bias, in each bin, we compute the standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid. The measurement errors are shown in Figure \ref{fig:meas_err} as contours.

@@

After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left. Then we match them to the LSBG catalog (described in Section \ref{sec:detection}) as follows. For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}. It turns out that 40\% of hosts have virial radii larger than 300 kpc. Then we identify any LSBG that falls into the projected angular virial radius of the host. If one LSBG is matched to multiple hosts, we assign it to the nearest host based on the separation normalized by host virial radius. Finally, we have 901 MW-like hosts and 10,579 LSBG candidates associated with them. However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shredded large galaxies, compact sources in galaxy outskirts, etc. As introduced in Section \ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects. There are 2,673 objects left after the deblending cuts. Next, we model them using the Spergel profile as described in Section \ref{sec:modeling}. Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives. We also remove duplicated objects. In the end, we have 2510 LSBG candidates as our final LSBG sample, from which we construct the ultra-diffuse galaxy (UDG) sample and the ultra-puffy galaxy (UPG) sample as follows.

\subsection{UDG and UPG sample}\label{sec:sample}
The UDG population is usually defined based on the surface brightness and the physical size of the galaxy. However, there are many different criteria in literature: \citep{vanDokkum2015} define UDGs to have effective radius $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}, and the size criterion also varies from $>1$ kpc to $>1.5$ kpc. \citet{vanNest2022} explore these definitions and find that different choice of UDG could drastically affect which subset of dwarfs are selected, therefore affect our understanding of the UDG population.

The measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020} or other contaminants. Therefore in this work, we use the average surface brightness within effective radius $\sbeff$ to define UDG. The difference between the average surface brightness and the central surface brightness for \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$. Since dwarf galaxies and UDGs typically has \sersic{} index in a range of $0.8 < n < 1.2$ \citep{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value. In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, which takes the measurement errors into account. This definition maximizes the consistency with the definition in \citet{vanDokkum2015} while not losing UDGs harboring nuclear star clusters.

Among the 2510 LSBG candidates, there are 459 objects satisfying the UDG definition. We did a final visual inspection for these objects and excluded 16 objects that are very likely to be false positives. We also removed another 8 objects having completeness less than 0.1. In the end, we obtain our UDG sample with 435 objects. The UDG catalog is available and shown in Table \ref{tab:catalog}.

\vspace{1em}

The concept of UDG was proposed for those dwarf galaxies with large physical size and diffuse light distribution. However, the size of a galaxy is strongly correlated with its mass, as known as the mass-size relation \citep[e.g.,][]{Lange2015}. The slope of the mass-size relation has been shown to be color-dependent for galaxies above $M_\star > 10^{8.5}\ M_\odot$: blue star-forming galaxies have a shallower slope, whereas red quenched galaxies have a steeper slope. However, recent works show that the mass-size relation in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$) is quite universal: the slope and intercept are not sensitive to the color and morphology of dwarf galaxy \citep{ELVES-I}. This gives us a chance to define a subset of dwarf galaxies that are outliers on the mass-size plane. Taking the measured mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the mass-size relation. The UPGs are not necessarily large in physical size or faint in average surface brightness. Both UDG and UPG represent subsets of dwarf galaxies that are larger and diffuser than average. However, the hard cut on size (1.5 kpc) makes UDG losing ``large'' galaxies at the low-mass end because as mass goes smaller, the average size also gets smaller. The surface brightness cut of UDG also biases the UDG sample in color distribution and further bias the quenched fraction, as will be discussed in Section \ref{sec:quench}. The definition of UPG based on the observed mass-size relation is more physics-motivated, and UPG better represents a homogeneous subset of dwarf galaxies along the stellar mass axis. There is also no color preference in the UPG definition for a given stellar mass. It is worth noticing that definition based on mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.

There are 392 objects in our LSBG candidates satisfying that they are $1.5\sigma$ above the ridge line of the mass-size relation. After visual inspection and removing objects with completeness less than 0.1, we have 363 galaxies in our UPG sample. The distribution of the UDG and UPG sample on the size-surface brightness plane are shown in Figure \ref{fig:udg_upg_re_mu}. The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively. Two marginal plots show the unnormalized histograms of galaxies in the two color bins. The numbers of red and blue galaxies are similar in the UDG sample, but there are more blue galaxies than red ones in the UPG sample. Since there is no hard surface brightness cut, the UPG sample includes a lot of blue galaxies with higher surface brightness ($\sbeff < 25$). The UPG sample also lose a significant fraction of red galaxies at $25 < \sbeff < 26$, because they are not LSB (hence low-mass) enough to be higher than $1.5\sigma$ from the mass-size relation.

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{udg_upg_sample.pdf}
	}
    \caption{The distribution of galaxies in the ultra-diffuse galaxy (UDG) sample (\textit{left}) and the ultra-puffy galaxy (UPG) sample (\textit{right}). The UDGs are galaxies with $r_e>1.5$ kpc and $\sbeff > 25.0\sbunit$. The UPGs is defined to be $1.5\sigma$ above the mass-size relation in \citet{ELVES-I}. We split the samples into two color bins and show them in red ($g-i>0.8$) and blue ($g-i<0.8$). The marginal histograms are not normalized to highlight the relative number of red and blue galaxies. Compared with the UDG sample, the UPG sample includes blue galaxies with surface brightness higher than the UDG cut ($\sbeff < 25\ \sbunit$) and excludes red galaxies at $25 < \sbeff < 26\ \sbunit$.
    }
    \label{fig:udg_upg_re_mu}
\end{figure*}

\vspace{1em}

% Write about mass calculation, extinction correction, etc.
We only corrected measured colors for Galactic extinction based on \citet{SFD1998,Schlafly2011}.

\subsection{Background contamination}

\section{Results}

\citet{Trujillo2020}: define size based on surface mass density

@@

SBeff relation with SB0: Yagi, Graham

@@

\subsection{Quenched fraction}\label{sec:quench}

\citep{Baxter2021}

\citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.\citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
	}
    \caption{Caption}
    \label{fig:mass_size}
\end{figure*}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{quenched_frac_dist2host.pdf}
	}
    \caption{Caption}
    \label{fig:qfrac_dist2host}
\end{figure*}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
	}
    \caption{Caption}
    \label{fig:qfrac_host_color}
\end{figure*}

@@

\begin{table}
\caption{UDG (UPG) catalog description} 
\label{tab:catalog}
\begin{center}
\begin{tabular}{l l l}
\hline\hline
% \multicolumn{3}{c}{Table: LSBGs (781 rows)}                 \\
% \hline
Column Name      & Unit    & Description                    \\
\hline
ID                       &         & Unique LSBG ID \\
ra                       & deg     & Right ascension (J2000) \\
dec                      & deg     & Declination (J2000) \\
$r_e$         & arcsec  & Circularized effective radius  \\
$\sigma(r_e)$ & arcsec  & Uncertainty of $r_e$ \\
$\overline{\mu}_{\mathrm{eff}}(g)$               & $\sbunit$ & $g$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(g))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(g)$           \\
$\overline{\mu}_{\mathrm{eff}}(r)$               & $\sbunit$ & $r$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
$\overline{\mu}_{\mathrm{eff}}(i)$               & $\sbunit$ & $i$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
$m_g$                    & mag     & $g$-band apparent magnitude     \\
$\sigma(m_g)$            & mag     & Uncertainty of $m_g$            \\
$m_r$                    & mag     & $r$-band apparent magnitude     \\
$\sigma(m_r)$            & mag     & Uncertainty of $m_r$            \\
$m_i$                    & mag     & $i$-band apparent magnitude     \\
$\sigma(m_i)$            & mag     & Uncertainty of $m_i$            \\
$g-r$                    & mag     & $g-r$ color                     \\
$\sigma(g-r)$           & mag     & Uncertainty of $g-r$ color      \\
$g-i$                    & mag     & $g-i$ color                     \\
$\sigma(g-i)$           & mag     & Uncertainty of $g-i$ color      \\
$\nu$                    &         & Spergel index              \\
$\varepsilon$               &         & Ellipticity                     \\
$A_g$                    & mag     & $g$-band Galactic extinction \\
$A_r$                    & mag     & $r$-band Galactic extinction \\
$A_i$                    & mag     & $i$-band Galactic extinction \\
comp & & Completeness \\
%Host information (ra, dec, Mstar, distance to host, Rvir, g-i) \\
\hline\hline
\end{tabular}
\end{center}
\tablecomments{
These tables are published in their entirety in machine-readable format.
Magnitudes are on the AB system and have not been corrected for Galactic
extinction. We provide Galactic extinction corrections, which are derived from
the \citet{Schlafly2011} recalibration of the \citet{SFD1998} dust maps. 
}
\end{table}

Also add external link for fake UDG catalog, etc.
